---
title: "Lab-7-kermit-gracie"
author: "Gracie White"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Gracie's first message in the document. Hi Gage. 

sup nerd

If you are the collaborator
- load the tidyverse
- read in the kermit data as 'kermit'
- make some side-by-side histograms of the Score.pre for all respondents, separated by the Gender column

```{r}
library(tidyverse)

kermit <- read_csv("kermit.csv")
```

```{r}
kermit_hist <- ggplot(kermit, aes(x = Score.pre)) +
  geom_histogram(bins = 4) +
  facet_wrap(~Gender)

kermit_hist
```


Perform a rank-based test 

perform rank based comparisions using a mann-whitney u and and wilcoxon-signed rank?


Is there a significant diference in pre-talk ranks of kermit for Male and Female respondents

mwu_kermit <- kermit %>%
wilcox.test(Score.pre ~ Gender, data =.)

#Null: there is not a significant difference in ranks for male and female respondants
#Alt: there is a significiant difference

mwu_kermit

